---
title: "Accessing Coin Gecko's API for Cryptocurrency Market Data"
author: "Chad Dulle"
date: "2023-07-27"
output: html_document
---

Here I will give some simple examples of using Coin Gecko's API to access market data for the broad cross-section of cryptocurrencies and tokens from various blockchains. Coin Gecko offers a basic subscription that is free to use for everyone interested in learning more about cryptocurrency data

### Load Packages
```{r warning=FALSE, message=FALSE,eval=FALSE}
# Install Packages
install.packages('tidyverse')
# Load Packages
library(tidyverse)
library(httr)
library(jsonlite)
library(glue)
```

### A Basic GET Call
Set the generic URL that can be used in conjunction with any of Coin Gecko's endpoints to make a GET call. In lamen's terms, a GET call is your computer asking the API to grant you access to a particular dataset (i.e. an "endpoint").
```{r,eval=FALSE}
# Base URL
base <- 'https://api.coingecko.com/api/v3/'
```

We will use this as a simple example of a single GET call. For this endpoint (coins/list), we will be getting every cryptocurrency/token that is available on CoinGecko's API
```{r get assets,eval=FALSE}
##### List all assets #####  

  # set endpoint
  endpoint <- 'coins/list'

  # GET call
  get <- GET(glue(base,endpoint))
  # prepare data
  dat <- fromJSON(rawToChar(get$content))
  # view data
  df1 <- data.frame(name=dat$name,ticker=dat$symbol,id=dat$id)
  # vector of all asset IDs
  IDs <- df1$id
```